---
title: "lum_cont_comp"
author: "VB"
date: "14/06/2022"
output: html_document
---

loads the file with the image list and all specs and calculates average luminance, contrast, and complexity for each image category (pleasaant, unpleasant, neutral images)

```{r}
base_dir <- "/Users/valeria/Desktop/ValeriaDocs/lab2020/alphaflick/psychopy/alphaflick_experiment"
filepath <- file.path(base_dir,"piclist.csv") # construct the file name

imagefile <- read.csv(filepath, header = TRUE, sep = ",", 
         dec = ".")
#getwd()
```

calculate average INTACT luminance, contrast, and compexity:

```{r}

image_lum_long <- pivot_longer(imagefile,
                                      cols = mean_lum_intact_Blue:mean_lum_intact_Green:mean_lum_intact_Red,
                                      names_to = "luminance", 
                                      values_to = "units") %>%
  
                                group_by(image_id) %>%
                                summarise(mean_lum=mean(units)) # average across 3 lum channels for each image
                               
image_cont_long <- pivot_longer(imagefile,
                                      cols = std_intact_B:std_intact_R,
                                      names_to = "contrast", 
                                      values_to = "units") %>%
  
                                group_by(image_id) %>%
                                summarise(mean_contrast=mean(units)) # average across 3 lum channels for each image
  

image_complex_long <- pivot_longer(imagefile,
                                      cols = complexity,
                                      values_to = "rating") %>%
  
                                group_by(image_id) %>%
                                summarise(mean_complexity=mean(rating)) # average across 3 lum channels for each image
  

```

calculate average SCRAMBLED luminance, contrast:

```{r}

image_scr_lum_long <- pivot_longer(imagefile,
                                      cols = mean_lum_scr_Blue:mean_lum_scr_Red,
                                      names_to = "scr_luminance", 
                                      values_to = "units") %>%
  
                                group_by(scrambled) %>%
                                summarise(mean_lum=mean(units)) # average across 3 lum channels for each image


image_scr_cont_long <- pivot_longer(imagefile,
                                      cols = std_scr_B:std_scr_R,
                                      names_to = "scr_contrast", 
                                      values_to = "units") %>%
  
                                group_by(scrambled) %>%
                                summarise(mean_contrast=mean(units)) # average across 3 lum channels for each image
 
```

join things up for scrambled and intact:

```{r}
# for scrambled:
 image_scr_lum_long %>%
         left_join(image_scr_cont_long, by = c("scrambled")) -> lum_cont_scr

# for intact:
image_lum_long %>%
  left_join(image_cont_long, by = c("image_id")) %>%
  left_join(image_complex_long, by = c("image_id")) -> lum_cont_compl_intact
```

calculate mean lum, contrast, complexity for each emo category separately:

```{r}

# for scrambled:
lum_cont_scr_condavg <- lum_cont_scr %>%
                        mutate(emotion = 
                                 ifelse(grepl("en", lum_cont_scr$scrambled), "neutral", # write neutral
                                        ifelse(grepl("eu", lum_cont_scr$scrambled), "unpleasant", "pleasant") # write unpleasant, otherwise pleasant
                                        ) 
                              ) %>%
                        group_by(emotion) %>%
                        summarise(lumavg=mean(mean_lum), contavg=mean(mean_contrast))


# for intact:
lum_cont_compl_condavg <- lum_cont_compl_intact %>%
                        mutate(emotion = 
                                 ifelse(grepl("en", lum_cont_scr$scrambled), "neutral",
                                        ifelse(grepl("eu", lum_cont_scr$scrambled), "unpleasant", "pleasant")
                                        ) 
                              ) %>%
                        group_by(emotion) %>%
                        summarise(lumavg=mean(mean_lum), contavg=mean(mean_contrast), complavg=mean(mean_complexity))

```

grandmeans:

```{r}
lum_cont_scr_condavg %>% 
  summarise(scr_lumgrandavg = mean(lumavg), scr_contgrandavg = mean(contavg))

lum_cont_compl_condavg %>% 
  summarise(int_lumgrandavg = mean(lumavg), int_contgrandavg = mean(contavg), int_complgrandavg = mean(complavg))
```

